Numerical modelling of the Cordilleran ice sheet

### 2014-08-25 kappa.tex
Add space for acknowledgements.
Disable colour links.
Add acknowledgements.

% load packages
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{bm}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage{physics}
\usepackage[colorlinks, citecolor=blue]{hyperref}
\usepackage[sort]{cleveref}  % needs to be loaded after hyperref
\usepackage{doi}  % needs to be loaded after hyperref
\usepackage{graphicx}
\usepackage{multicol}
\graphicspath{{figures/}}
\nobibliography*

@@

% Some general low-priority todos
% -- use latex in matplotlib figures
% -- homogeneize subfig label fonts
% -- add software references
% -- add Swedish abstract
% -- add numerical implementation

@@

% References
\renewcommand{\urlprefix}[0]{}  % remove default "URL" prefix
\bibliographystyle{copernicus}
\bibliography{refs/references.bib}

>>>>

% load packages
\usepackage{amsmath}
\usepackage{bibentry}
\usepackage{bm}
\usepackage[utf8]{inputenc}
\usepackage[T5, T1]{fontenc}
\usepackage{natbib}
\usepackage{physics}
\usepackage[hidelinks]{hyperref}
\usepackage[sort]{cleveref}  % needs to be loaded after hyperref
\usepackage{doi}  % needs to be loaded after hyperref
\usepackage{graphicx}
\usepackage{multicol}
\graphicspath{{figures/}}
\nobibliography*

@@

@@

% References
\renewcommand{\urlprefix}[0]{}  % remove default "URL" prefix
\onecolumn
\begin{multicols}{2}  % ensure levelled end-of-text
\bibliographystyle{copernicus}
\bibliography{refs/references.bib}
\end{multicols}

% ======================================================================
\clearpage
\thispagestyle{plain}
\hfill \textbf{\huge Acknowledgements}
\vfill
% ======================================================================

\noindent This work would not have been possible without the help and
involvement of many friends and colleagues. I am grateful to Arjen Stroeven, my
main supervisor, for his continuous support through good and bad times. I most
particularly thank him for his scrutinized work and tough criticism on all my
texts, which is hopefully reflected in the quality of this thesis. I also would
like to thank Irina Rogozhina for her fearless jump into my supervising team
last year and constant support since then. She has been a great mentor, a good
friend and a fantastic colleague, and I hope that we will continue to work
together. I thank Qiong Zhang for her positiveness and encouragement, technical
help with meteorological data and useful advice in my early writing steps, and
Johan Kleman for few but always inspiring discussions.

I also wish to particularly thank Jakob Heyman and Martin Margold, who have
been great tutors on glacial geomorphology and many other things during the
first years of my PhD. Likewise, I am immensely grateful to Ed Bueler and
Constantine Khroulev for dedicated support on PISM during the last three years
and for precious advice during my short visit at the University of Alaska
Fairbanks.

To my office mates; Carl Lilja, Markus Nathansson, Ping Fu and Natacha
Gribenski; thank you for cultivating a friendly working atmosphere. I also wish
to thank colleagues from the glaciology group for many entertaining paper
discussions, empowered by the incorruptible commitment and delicious cookies of
Patrick Applegate. Thanks to the administrative staff, and most particularly
Susanna Blåndman, Carina Henricksson and Linus Richert, for having been
constantly available for help, as well as to Helle Skånes, for guiding me
through the last steps towards my doctoral defense.

To colleagues from the German Research Centre for Geosciences, and especially
to Maik Thomas, Jorge Bernales and Tonio; thank you for supporting my visit and
welcoming me in Potsdam. To Ola Fredin and Lena Rubensdotter; thank you for
introducing me to glacial geology during my stay in Trondheim in 2008, for
encouraging me to pursue this path and for unforgettable fieldwork memories.

To my friends from Stockholm and Potsdam; Max, Nathalie, Juri, Lisa, Reto,
Peng, Ying, Nikki, Thomas, Viola; thank you for making these years enjoyable.
Finally, I thank my family, and most specially my parents Lydie and Christophe,
for having given me the chance to pursue a higher education, and for all those
summers spent mountain-hiking in the Alps.
{\fontencoding{T5}\selectfont Th\h{u}y}, your determination to push me to the
finish line had no limits. Thank you for providing this amazing support, and
for sharing my frustrations and my joys along the way.

\bigskip
\noindent\textbf{Funding sources}

\noindent My salary was provided by Stockholm University, and research grants
from the Swedish Research Council (VR) and the German Academic Exchange Service
(DAAD). Additional funds for conference participations, course attendances,
collaborative travels and fieldwork were provided by the Carl Mannerfelt Fund,
the Bolin Centre for Climate Research, the Ahlmanns and Lagrelius Funds for
Geographic Research, the De Geer Foundation for Quaternary Research and the
Wallenberg Foundation.
